Methodology for Assessing the State of the Practice for Domain X

### 2020-10-23 StateOfPractice/Methodology/Methodology.tex
updated Section 4 Methodology based on comments

\begin{enumerate}	
	\item The domain must fall within the research software scope.
	\item The domain must be well understood.
	\item There must be a community of people studying the domain.
	\item A preliminary search, or discussion with experts, suggests that there will be numerous, at least about 15, candidate software packages to study.
	\item The software packages must have open source options. 
\end{enumerate}

Some examples of domains that fit these criteria are seismology software, as well as mesh generators and processors. These are described in \citep{SmithEtAl2018} and \citep{smith2016state}, respectively.

>>>>

\begin{enumerate}	
	\item The domain must have a well-defined, stable theoretical underpinning. Standard textbooks, preferably understandable by an upper undergraduate student, is a good sign of this.
	\item There must be a community of people studying the domain.
	\item The software packages must have open source options. 
	\item A preliminary search, or discussion with experts, suggests that there will be numerous, at least about 15, candidate software packages in the domain that qualify as `research software'.
\end{enumerate}

Some examples of domains that fit these criteria are finite element analysis, quantum chemistry, seismology, as well as mesh generators and processors. These are described in \citep{szabo1996finite}, \citep{veryazov20042molcas}, \citep{SmithEtAl2018} and \citep{smith2016state}, respectively.
